Climate REDIAM

### 2017-06-19 analysis/analysis_climate.Rmd
update climate

---
title: "Analysis of Competence Index"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Feb"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: references.bib 
csl: ecology.csl
---

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("stringr")
```

@@

```{r, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

# density data 
compete <- read.csv(file=paste0(di, '/data_raw/dendro_competence.csv'), header=TRUE, sep=',')
```

>>>>

---
title: "Climate REDIAM"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017"
output:  
  md_document:
    toc: true
    variant: markdown_github
bibliography: references.bib 
csl: ecology.csl
---

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("stringr")
library("lubridate")
```

@@

```{r, echo=FALSE}
# machine <- 'ajpelu'
machine <- 'ajpeluLap'
di <- paste('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

# climate data

cli <- read.csv(file=paste0(di, '/data_raw/meteo/5514_base_aerea_dialy.csv'), header=TRUE, sep=',')
```

# Minimun temperature
```{r}

cli %>% 
  filter(vb == 'TD4') %>% 
  mutate(y = lubridate::year(date)) %>% 
  filter(value > 34) %>% 
  group_by(y) %>% 
  summarise(ndays = n()) %>% 
  ggplot(aes(x=y, y=ndays)) +
  geom_point() + 
  geom_smooth(method = 'loess', span = 0.75, se=FALSE) +
  theme_bw()

+ 
  geom_vline(xintercept = 1995)

  group_by(y) %>% 
  slice(which.max(value))

df %>% group_by(A) %>% slice(which.min(x)
